---
title: "FancyPackRLiU6"
author: Jun Li
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FancyPackRLiU6}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Description
The package presents three typical ways of resolving Knapsack problem, with brutal force, dynamic programing and approximate solutions. By means of exploring different computing complexities, a better understanding of fast code has been reached.

## Fields
*x*, a data frame of items with different values and weights

*W*, the capacity of knapsack

## Return
a list with best value and selected elements 


## Questions
```{r setup, echo=TRUE}
library(FancyPackRLiU6)
set.seed(42)
n<- 2000
knapsack_objects <-data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000))

## Question How much time does it takes to run the algorithm for n = 16 objects?
start<-proc.time()
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500) 
end<-proc.time()
(end-start)[2]   ## 0.06
## Question How much time does it takes to run the algorithm for n = 500 objects?
start<-proc.time()
knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500)[2] 
end<-proc.time()
(end-start)[2]   ## 0.02
## Question How much time does it takes to run the algorithm for n = 1000000 objects?
set.seed(42)
n<- 1000000
knapsack_objects <-data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000))
start<-proc.time()
system.time(greedy_knapsack(x = knapsack_objects, W = 3500))[2] 
end<-proc.time()
(end-start)[2]   ## 0.01
## Question What performance gain could you get by trying to improving your code?
    ## lineprof show that binary convertion is one of the biggest bottleneck, and a suggestion is presented in the next question
## Question What performance gain could you get by using Rcpp and C++?
start<-proc.time()
brute_force_knapsack(x = knapsack_objects[1:16,], W = 3500,fast=TRUE) 
end<-proc.time()
(end-start)[2]   ## 0.05, Rcpp function improved performance with almost 17% faster 
## Question What performance gain could you get by parallelizing brute force search? 
    ##
```